---
# ---------- General:
RemovePreprintSubmittedTo: False  # Removes the 'preprint submitted to...' at bottom of titlepage
Journal: "Journal of Finance"   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: FALSE                       # Add a table of contents
numbersections: TRUE             # Should sections (and thus figures and tables) be numbered?
fontsize: 12pt                  # Set fontsize
linestretch: 1.2                # Set distance between lines.
link-citations: TRUE            # This creates dynamic links to the papers in reference list.

title: "Question 1"

output:
  html_document:
    keep_tex: TRUE
    #template: Tex/TexDefault.txt
    fig_width: 4.5 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5
abstract: |
  This investigates how Africa's experience differed from the other regions; it investgates what it means to have certain attributes as well as looks at what the implications should new vaccinations have been rolled out later.
---

```{r setup, include=FALSE }
knitr::opts_chunk$set( echo = TRUE)
knitr::opts_knit$set(root.dir= "~/Practical data science 2023/22574646/data/Covid")
library(tidyverse)
library(purrr)
library(ggplot2)
library(lubridate)
library(ggpubr)
library(ggthemes)
library(reshape2)

```

# The main Data

The main Data that I'll be working on are loaded in here.

```{r Main datatsets}


#loading in the main database I'll be using

owid_covid_data <- read_csv("owid-covid-data.csv")#load in the data 

attach(owid_covid_data) #attach data so don't have to call it each time


```

# The African experience

Africa experienced lower deaths rates (Covid 19 deaths rates) and new cases than the other regions.

```{r Africa Experience with covid-19}



#The following code summarizes evidence that is grouped by locations and continent


owid_sum<-owid_covid_data %>% group_by(continent) %>% summarise_at( vars(c(new_cases_per_million, new_deaths_per_million, total_deaths_per_million, total_deaths, total_cases, total_cases_per_million)), ~mean(.x,na.rm=T))


Owid_summarized<- owid_covid_data %>% arrange(date) %>%group_by(location, continent) %>%  summarise_at(vars(c(new_cases_per_million, new_deaths_per_million, total_deaths_per_million, hospital_beds_per_thousand, total_cases,total_cases_per_million, weekly_hosp_admissions, weekly_hosp_admissions_per_million)),~mean(.x,na.rm=T))



#Assign colours to different grouped positons
cols<-c ("blue", "orange", "purple", "gold", "pink", "green","yellow") 


#Draws a barplot of owid_sum


g<-owid_sum %>% ggplot()+ geom_bar(stat="identity",aes(x=continent, y=new_cases_per_million),alpha=0.8)+
    scale_color_manual(values=cols)

g


#Plot the graph for total deaths
         
plt<-Owid_summarized%>% group_by(continent) %>%ggplot()+
    geom_point(aes(x=location, y=total_deaths_per_million,size=total_deaths_per_million, colour=continent))+
    scale_color_manual(values = cols)+
    theme(axis.title.x= element_blank(), axis.text.x =element_blank(),axis.ticks.x = element_blank(), axis.title.y = element_text("Total deaths per million"))+ ggtitle(label = "Overall pictures") 


plt


```

#Do countries with higher life_expectancy display distinct patterns in the severity of their covid-19 experience

Question: Do countries with higher life expectancy display distinct patterns in the severity of their covid-19 experience

Motivation: life expectancy is suggestive of healthy population and good medical care hence, should show tendency of lower deaths rates

Method: Distribution of death amongst those above the mean/ average life expectancy in the data and those below IT

Findings: Both have tails to the right (skewed to the right), however, those whose life expectancy are higher than the average, have a flatter distribution than those whose life expectancy are smaller.

Conclusion: I suspect it has to do something with good health care

```{r Do countries with higher life expectancy display distinct patterns in the severity of their Covid experience}

#idea is what is the mean in data and work around that for each variables 


#I summarized the data by their locations for the variables totcal deaths and cases and life expec
Summarized_locations<-owid_covid_data %>% group_by(location) %>% 
    summarize_at(vars(c(total_cases_per_million,total_deaths_per_million, life_expectancy)),~mean(.x, na.rm=T))


#I added columns which took the mean of the life expectancy from groups and made a criteria for those who are above it and those below it
Ungrouped_mutated<-Summarized_locations %>% ungroup() %>% mutate(life_expect= mean( life_expectancy, na.rm=T)) %>%
    mutate(criteria=ifelse(life_expectancy<life_expect, "smaller", ifelse(life_expectancy>life_expect, "higher", "middle"))) %>%
    drop_na()


#Plot the graphs
Deaths<-Ungrouped_mutated %>% group_by(criteria) %>% ggplot(aes(x=total_deaths_per_million)) + geom_density(aes(fill=criteria))+
    theme(title=element_text("Total deaths per million for two groups with different life expectancy"), axis.title.x= element_text("Total deaths per million"), axis.title.y =element_text("Probabilties"))

Deaths

```

# How quickly different regions increased their hospitalization facilities and whether this led or lagged ICU admissions

If they had not increased it fast enough, this wouldn't have resulted in low ICU admissions.

```{r How quickly different regions increased their hospitalization facilities, and whether this led or lagged ICU admissions}

#For this I used hospital bed per one thosuand and dates 

#Calculate the data for new vaccines rollout and ict 


#Create new data with the specfic variables I need and drop all the na's 
Data3<-owid_covid_data %>% group_by(location) %>% select(iso_code, date, location, continent, new_vaccinations_smoothed_per_million, weekly_icu_admissions_per_million) %>%
 mutate(lead_lags=ifelse(lead(weekly_icu_admissions_per_million)>weekly_icu_admissions_per_million,"leads","lags")) %>%
     mutate(Time_passed=lead(date)-min(date)) %>%drop_na()



#graphs the variables 
attach(Data3)

Data3 %>%
ggplot()+geom_line(aes(x=as.numeric(Time_passed),y=weekly_icu_admissions_per_million,color=location), size=1)+
    ggtitle(label="How quickly they update/ vaccine rollouts")+
    xlab("Time passed")+
    ylab("ICU admission")




```
