---
title: "Question 3"
#output: html_document
date: "2023-06-16"


# IMPORTANT: Change settings here, but DO NOT change the spacing.
# Remove comments and add values where applicable.
# The descriptions below should be self-explanatory

#title: "Helping You Write Academic Papers in R using Texevier"
#subtitle: "This will appear as Right Header"

documentclass: "elsarticle"


# ---------- General:
RemovePreprintSubmittedTo: False  # Removes the 'preprint submitted to...' at bottom of titlepage
Journal: "Journal of Finance"   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: FALSE                       # Add a table of contents
numbersections: False            # Should sections (and thus figures and tables) be numbered?
fontsize: 12pt                  # Set fontsize
linestretch: 1.2                # Set distance between lines.
link-citations: FALSE            # This creates dynamic links to the papers in reference list.

### Adding additional latex packages:
# header-includes:
#    - \usepackage{colortbl} # Add additional packages here.

output:
 html_document:
    keep_tex: TRUE
    #template: Tex/TexDefault.txt
    fig_width: 4.8 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5
abstract: |
  This report compares coldplay and mettalic's style of music. Coldplay's music attempts to be balanced across all genres while Mettalic puts more weight on other aspect of his music.
---

```{r setup, include=FALSE }
knitr::opts_chunk$set( echo = TRUE)
knitr::opts_knit$set(root.dir= "~/Practical data science 2023/22574646/data/Coldplay_vs_Metallica")


#The libaries needed
library(ggplot2)
library(ggpubr)
library(lubridate)
library(tidyverse)
library(reshape2)

```

# Loading The data

I load the data in this chunk.

```{r}
coldplay<-read.csv("Coldplay.csv")
metallica<- read.csv("metallica.csv")

```

# Exploring their styles: A summary

The box plot below are displayed for danceability, energy, speechiness, acousticness, instrumentalness, liveness, and valence for coldplay and metallica. With respect to Coldplay's music, the distribution is generally quite skewed to the right for accousticness, liveness and instramentalness whilst the remaining variables are symmetrical. Overall, coldplay's music aims to giving listener a feel of everything. Metallica on the other hand (in blue), various alot on these variables across their album. Although, they are less big on enegry, acousticness and speechiness.

```{r}

#The pre-editing
vec_coldplay<-colnames(coldplay)[-c(1,4,3,5,2,6,13,12,14)] #columns which are abandoned
coldplay_trimmed<- select(coldplay,vec_coldplay) #selecting specific variables

vec_metallica<-colnames(metallica)[-c(1,2,3,5,14,4,8)] #columns abandoned 
metallica_trimmed<- select(metallica,vec_metallica) #selecting specific variables


#For comparability sake (put them on one plot)
par(mcol=c(2,2))
boxplot(coldplay_trimmed,use.cols=TRUE,border="pink") #Drawing a boxplot for coldplay
boxplot(metallica_trimmed,use.cols=T,border="blue",pars=list(boxwex=0.8)) #Drawing a boxplot for Metallica



```
