---
title: "Question 2"
#output: html_document
date: "2023-06-16"

# IMPORTANT: Change settings here, but DO NOT change the spacing.
# Remove comments and add values where applicable.
# The descriptions below should be self-explanatory


# ---------- General:
RemovePreprintSubmittedTo: FALSE  # Removes the 'preprint submitted to...' at bottom of titlepage
Journal: "None"   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: FALSE                       # Add a table of contents
numbersections: FALSE             # Should sections (and thus figures and tables) be numbered?
fontsize: 11pt                  # Set fontsize
linestretch: 1.2                # Set distance between lines.
link-citations: False            # This creates dynamic links to the papers in reference list.

### Adding additional latex packages:
# header-includes:
#    - \usepackage{colortbl} # Add additional packages here.

output:
  html_document:
    keep_tex: TRUE
    #template: Tex/TexDefault.txt
    fig_width: 3.5 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5
abstract: |
 According to the internet, a warm day is around 20-24 degree celusiuis. I use this to inform my judgement on whether England was cold or warm. In turns out that it is quite cold hitting temparatures as low as -11.80. An normal day in england is in fact not so warm as the histogram shows below.
 
---

```{r setup, include=FALSE }
knitr::opts_chunk$set( echo = TRUE)
knitr::opts_knit$set(root.dir= "~/Practical data science 2023/22574646/data/London")


#The libaries needed
library(ggplot2)
library(ggpubr)
library(lubridate)
library(tidyverse)
library(reshape2)
```

#The code

The summary statistics shows us that it can get pretty cold (-6.20 and -11.80). Compared to other places, it is not as warm (at only 37.90).s


```{r Importing the data}

london_weather<- read.csv ("london_weather.csv") #loads the data
summary(london_weather) #summarizes the main statistics 


```


#A graph of what a typical london day looks like 
On the internet it said that a cool day is around 20-24 degree's Celsius whilst anything above 29 is too hot. If one looks at a typical day in London (the temperature on average over the years), for the majority London is a cold country. The majority of the time it is called.



```{r fig.height = 3, fig.width = 5}
hist(london_weather$mean_temp, prob=T,col="lightblue",main= "Spread of average tempatures over the years",ylab="Probabilities",xlab="A Typical London day") #calculates the histograms
lines(density(london_weather$mean_temp, na.rm = T),col=10,lwd=2) #adds the density function
abline(v=20,col="red",lwd=3,lty=2) #adds the cutoff

```

